Rclean: A Tool for Writing Cleaner, More Transparent Code

### 2020-02-04 joss/paper.Rmd
Adds examples for other functions

script.long <- system.file(
    "example", 
    "long_script.R", 
    package = "Rclean")
script <- script.long
```

@@

As you can see, `Rclean` has picked through the tangled bits of code
and found the minimal set of lines relevant to our object of
interest. This code can now be visually inspected to adapt the
original code or ported to a new, "refactored" script.

```{R ex-keep}

@@

```{R ex-get_vars}

@@

```{R ex-code_graph}

@@

@@

>>>>

script.long <- system.file(
    "example", 
    "long_script.R", 
    package = "Rclean")
script <- script.long

@@

As you can see, `Rclean` has picked through the tangled bits of code
and found the minimal set of lines relevant to our object of
interest. This code can now be visually inspected to adapt the
original code or ported to a new, "refactored" script using `keep`.

```{R ex-keep, eval = FALSE}
fitSA <- clean(script, "fit_sqrt_A")
keep(fitSA)

@@

This will pass the code to the clipboard for pasting into another
document. To write directly to a new file, a file path can be
specified.

```{R ex-keep-write, eval = FALSE}
fitSA <- clean(script, "fit_sqrt_A")
keep(fitSA, file = "fit_SA.R")

@@

To explore more possible variables to extract, the `get_vars` function
can be used to produce a list of the variables (aka. objects) that are
created in the script.

```{R ex-get_vars-hid, eval = TRUE, echo = TRUE}

get_vars(script)

@@

Especially when the code for different variables are entangled, it can
be useful to visual the code in order to devise an approach to
cleaning. As seen above \@ref(fig:prov-graph), `code_graph` will
produce a visual of the code and the objects that they produce.

```{R ex-code_graph, fig.cap = "Example of the plot produced by the
code_graph function showing which lines of code produce which
variables and which variables are used by other lines of code."}

code_graph(script)

After examining the output from `get_vars` and `code_graph`, it is
possible that more than one object needs to be isolated. To do this is
simple in `keep` by passing the set of desired objects to the *vars*
argument.

```{R clean-mlti}

clean(script, vars = c("fit_sqrt_A", "fit_anova"))

Currently, because of the data provenance that is used, libraries can
not be isolated directly during the cleaning process. So, the
`get_libs` function provides a way to detect the libraries for a given
script. Just supply a file path and `get_libs` will return the
libraries that are called by that script.

@@

get_libs(script)
